# Applications

Some _significant_ applications are demonstrated in this chapter.

## Example one

```{r attr.source="style='display:inline-block;'", collapse=TRUE}
1:10  # a sequence from 1 to 10
10:1  # in the reverse order
```

<!--- :::: {style="display: flex;"} --->
:::: {style="display: grid; grid-template-columns: 1fr 1fr; grid-column-gap: 10px;"}

::: {}
Here is the **first** Div.

:::

::: {}
And this block will be put on the right:

:::

::::

## Example two

```{r, attr.source='.numberLines'}
if (TRUE) {
  x <- 1:10
  x + 1
}
```

```{r, attr.source='.numberLines startFrom="6"'}
if (TRUE) {
  1:10
}
```

## Example three

When you subset a data frame, it does not necessarily return
a data frame. For example, if you subset two columns, you get
a data frame, but when you try to subset one column, you get
a vector:

```{r class.source="bg-danger", class.output="bg-warning", echo=TRUE}
mtcars[1:5, "mpg"]
```

To make sure that we always get a data frame, we have to use
the argument `drop = FALSE`. Now we use the chunk option
`class.source = "bg-success"`.

```{r df-drop-ok, class.source="bg-success", echo=TRUE}
mtcars[1:5, "mpg", drop = FALSE]
```

```{r class.source="watch-out", echo=TRUE}
mtcars[1:5, "mpg"]
```

If you want to decorate individual elements in code blocks instead of the whole blocks, you may consider using the flair package: https://github.com/kbodwin/flair.
With this package, you can highlight different parts of your code (such as fixed strings, function names, and arguments) with custom styles (e.g., color, font size, and/or font weight).
